%% FIRST RENAME THIS FILE <yoursurname>.tex.
%% BEFORE COMPLETING THIS TEMPLATE, SEE THE "READ ME" SECTION
%% BELOW FOR INSTRUCTIONS.
%% TO PROCESS THIS FILE YOU WILL NEED TO DOWNLOAD asl.cls from
%% http://aslonline.org/abstractresources.html.


\documentclass[bsl,meeting]{asl}

\AbstractsOn

\pagestyle{plain}

\def\urladdr#1{\endgraf\noindent{\it URL Address}: {\tt #1}.}


\newcommand{\NP}{}
%\usepackage{verbatim}

\begin{document}
\thispagestyle{empty}

%% BEGIN INSERTING YOUR ABSTRACT DIRECTLY BELOW;
%% SEE INSTRUCTIONS (1), (2), (3), and (4) FOR PROPER FORMATS

\NP \absauth{Beibut Kulpeshov, Sergey Sudoplatov} \meettitle{On
algebras of binary formulas for weakly circularly minimal theories
}

\affil{Kazakh-British Technical University, Almaty, Kazakhstan}
\meetemail{b.kulpeshov@kbtu.kz}

\affil{Sobolev Institute of Mathematics, Novosibirsk State
Technical University, Novosibirsk State University, Novosibirsk,
Russia} \meetemail{sudoplat@math.nsc.ru}
%\urladdr{http://math.nsc.ru/$\sim$sudoplatov/}



\noindent

%% INSERT TEXT OF ABSTRACT DIRECTLY BELOW

Algebras of binary formulas are a tool for describing
relationships between elements of the sets of realizations of
1-types at binary level with respect to superpositions of binary
definable sets. We consider algebras of binary isolating formulas
originally studied in \cite{KScite1, KScite2}, where under a
binary isolating formula we understand a formula of the form
$\varphi(x,y)$, without parameters, such that for some parameter
$a$ the formula $\varphi(a,y)$ isolates some complete type from
$S_1(\{a\})$.

The notion of {\it weak circular minimality} was originally
studied in \cite{KScite3}. A {\it weakly circularly minimal
structure} is a circularly ordered structure $M=\langle M,
K_3,\ldots\rangle$ such that any definable (with parameters)
subset of $M$ is a union of finitely many convex sets in $M$. In
\cite{KScite4} countably categorical 1-transitive non-primitive
weakly circularly minimal structures of convexity rank 1 with
non-trivial definable closure have been described up to binarity.

Here we discuss algebras of binary isolating formulas for these
structures and give the following criterion for commutability of
such algebras:

\begin{theorem}
Let $M$ be a countably categorical $1$-transitive non-primitive
weakly circularly minimal structure of convexity rank $1$ with
${\rm dcl}(a)\ne \{a\}$ for some $a\in M$. Then the algebra
$\mathfrak{P}_{M}$ of binary isolating formulas is commutable iff
there exists an $\emptyset$-definable non-trivial monotonic-to-right bijection
on $M$.
\end{theorem}

This research has been funded by Science Committee of Ministry of
Education and Science of the Republic of Kazakhstan (Grant
No.~AP08855544), and by Russian Scientific Foundation (Project
No.~22-21-00044).

\begin{thebibliography}{10}

\bibitem{KScite1}
{\scshape  S.V.~Sudoplatov},{\bfseries\itshape Classification of
countable models of complete theories}, Novosibirsk, Edition of
NSTU, 2018.

\bibitem{KScite2}
{\scshape  I.V.~Shulepov, S.V.~Sudoplatov}, {\itshape Algebras of
distributions for isolating formulas of a complete theory},
{\bfseries\itshape Siberian Electronic Mathematical Reports},
Vol.~11 (2014), pp.~362--389.

\bibitem{KScite3}
{\scshape  B.Sh.~Kulpeshov, H.D.~Macpherson}, {\itshape Minimality
conditions on circularly ordered struc\-tures}, {\bfseries\itshape
Mathematical Logic Quarterly}, Vol.~51, No.~4 (2005),
pp.~377--399.

\bibitem{KScite4}
{\scshape B.Sh.~Kulpeshov}, {\itshape On $\aleph_0$-categorical
weakly circularly minimal struc\-tures}, {\bfseries\itshape
Ma\-the\-ma\-ti\-cal Logic Quarterly}, Vol.~52, No.~6 (2006),
pp.~555--574.






%% INSERT YOUR BIBLIOGRAPHIC ENTRIES HERE;
%% SEE (4) BELOW FOR PROPER FORMAT.
%% EACH ENTRY MUST BEGIN WITH \bibitem{citation key}
%%
%% IF THERE ARE NO ENTRIES
%% DELETE THE LINE ABOVE (\begin{thebibliography}{20})
%% AND THE LINE BELOW (\end{thebibliography})

\end{thebibliography}


\vspace*{-0.5\baselineskip}
% this space adjustment is usually necessary after a bibliography

\end{document}


%% READ ME
%% READ ME
%% READ ME

INSTRUCTIONS FOR SUPPLYING INFORMATION IN THE CORRECT FORMAT:

1. Author names are listed as First Last, First Last, and First
Last.

\absauth{FirstName1 LastName1, FirstName2 LastName2, and
FirstName3 LastName3}


2. Titles of abstracts have ONLY the first letter capitalized,
except for Proper Nouns.

\meettitle{Title of abstract with initial capital letter only,
except for Proper Nouns}


3. Affiliations and email addresses for authors of abstracts are
  listed separately.

% First author's affiliation
\affil{Department, University, Street Address, Country}
\meetemail{First author's email}
%%% NOTE: email required for at least one author
\urladdr{OPTIONAL}
%
% Second author's affiliation
\affil{Department, University, Street Address, Country}
\meetemail{Second author's email} \urladdr{OPTIONAL}
%
% Third author's affiliation
\affil{Department, University, Street Address, Country}
% Second author's email
\meetemail{Third author's email} \urladdr{OPTIONAL}


4. Bibliographic Entries

%%%% IF references are submitted with abstract,
%%%% please use the following formats

%%% For a Journal article
\bibitem{cite1}
{\scshape Author's Name}, {\itshape Title of article},
{\bfseries\itshape Journal name spelled out, no abbreviations},
vol.~XX (XXXX), no.~X, pp.~XXX--XXX.

%%% For a Journal article by the same authors as above,
%%% i.e., authors in cite1 are the same for cite2
\bibitem{cite2}
\bysame {\itshape Title of article}, {\bfseries\itshape Journal},
vol.~XX (XXXX), no.~X, pp.~XX--XXX.

%%% For a book


%%% For an article in proceedings
\bibitem{cite4}
{\scshape Author's Name}, {\itshape Title of article},
{\bfseries\itshape Name of proceedings} (Address of meeting),
(First Last and First2 Last2, editors), vol.~X, Publisher, Year,
pp.~X--XX.

%%% For an article in a collection
\bibitem{cite5}
{\scshape Author's Name}, {\itshape Title of article},
{\bfseries\itshape Book title} (First Last and First2 Last2,
editors), Publisher, Publisher's address, Year, pp.~X--XX.

%%% An edited book
\bibitem{cite6}
Author's name, editor. % No special font used here
{\bfseries\itshape Title of book}, Publisher, Publisher's address,
Year.
