\documentclass[bsl,meeting]{asl}

\AbstractsOn

\pagestyle{plain}

\def\urladdr#1{\endgraf\noindent{\it URL Address}: {\tt #1}.}


\newcommand{\NP}{}
%\usepackage{verbatim}

\begin{document}
\thispagestyle{empty}


\NP  
\absauth{Jos\'{e} M. M\'{e}ndez, Gemma Robles, Francisco Salto}
\meettitle{A class of implicative expansions of Belnap-Dunn logic in whose elements a Boolean negation is definable}
\affil{Universidad de Salamanca. Edificio FES, Campus Unamuno,
37007, Salamanca, Spain}
\meetemail{sefus@usal.es}
\urladdr{http://sites.google.com/site/sefusmendez}

\affil{Dpto. de Psicolog\'{i}a, Sociolog\'{i}a y Filosof\'{i}a, Universidad de Le\'{o}n, Campus Vegazana, s/n, 24071, Le\'{o}n, Spain}
\meetemail{gemma.robles@unileon.es}
\urladdr{http://grobv.unileon.es}

\affil{Dpto. de Psicolog\'{i}a, Sociolog\'{i}a y Filosof\'{i}a, Universidad de Le\'{o}n, Campus Vegazana, s/n, 24071, Le\'{o}n, Spain}
\meetemail{francisco.salto@unileon.es}


Let B$^{\prime}$ be the result of restricting Routley and Meyer basic relevant logic B (cf. \cite{RMPB}) as follows: (1) Restrict all axioms of B to rule form, except the self-identity axiom (i.e., $A\rightarrow A$), the distributive and the double negation axioms. (2) Restrict the rules Suffixing and Prefixing to the rule Transitivity. Then, we define the class of all C-extending implicative expansions containing B$^{\prime}$ of the well-known Belnap-Dunn logic in whose elements a Boolean negation is definable. We note that, apart from classical logic, in each one of these expansions the strong logic P\L 4 is definable. P\L 4 is equivalent to De and Omori's logic BD$_{+}$, Zaitzev's paraconsistent logic FDEP and B\'{e}ziau's 4-valued modal logic PM4N, according to \cite{DO15} (cf. \cite{RoMen21} and references therein).


\begin{thebibliography}{10}

\bibitem{DO15}
{\scshape M. De, H. Omori},
{\itshape Classical Negation and Expansions of Belnap–Dunn Logic},
{\bfseries\itshape Studia Logica}, 
vol. ~103 (2015), no. ~4, pp. 825–851.


\bibitem{RoMen21}
{\scshape G. Robles, J. M. M\'{e}ndez},
{\itshape A 2 set-up Routley-Meyer semantics for the 4-valued logic PŁ4},
{\bfseries\itshape 	Journal of Applied Logics ---IfCoLog Journal of Logics and their Applications},
vol. ~8 (2021), no. 10, pp. 2435-2446.

\bibitem{RMPB}
{\scshape R. Routley, R. K. Meyer, V. Plumwood, R. T. Brady},
{\bfseries\itshape Relevant Logics and their Rivals},
vol. 1
Atascadero, CA: Ridgeview Publishing Co.,
1982


\end{thebibliography}


\vspace*{-0.5\baselineskip}
% this space adjustment is usually necessary after a bibliography

\medskip
{\itshape Acknowledgements}. Work supported by research project PID2020-116502GB-I00, financed by the Spanish Ministry of Science and Innovation (MCIN/AEI/ \\ 10.13039/501100011033).

\end{document}


