%%FIRST RENAME THIS FILE <yoursurname>.tex. 
%%BEFORE COMPLETING THIS TEMPLATE, SEE THE "READ ME" SECTION BELOW FOR INSTRUCTIONS.
%% TO PROCESS THIS FILE YOU WILL NEED TO DOWNLOAD asl.cls from  http://aslonline.org/abstractresources.html. 

\documentclass[bsl,meeting]{asl}
\AbstractsOn
\pagestyle{plain}
\def\urladdr#1{\endgraf\noindent{\it URL Address}: {\tt #1}.}
\newcommand{\NP}{}
\usepackage{verbatim}

\begin{document}
\thispagestyle{empty}

%% BEGIN INSERTING YOUR ABSTRACT DIRECTLY BELOW; 
%% SEE INSTRUCTIONS (1), (2), (3), and (4) FOR PROPER FORMATS

\NP  
\absauth{Dorottya Szir\'aki}
\meettitle{Applications of the open dihypergraph dichotomy for generalized Baire spaces}
\affil{Alfr\'ed R\'enyi Institute of Mathematics, 
  Re\'altanoda u.~13--15, 
  H--1053 Budapest, Hungary}
\meetemail{dsziraki@renyi.hu}

%% INSERT TEXT OF ABSTRACT DIRECTLY BELOW

The open graph dichotomy 
for a given subset $X$ of the Baire space ${}^\omega\omega$ 
states that any open graph on $X$ either contains a large complete subgraph or admits a countable coloring. 
It is a definable version of the open coloring axiom for $X$ and it generalizes the perfect set property. 
Miller, Carroy and Soukup showed that several well-known results regarding
the second level of the Borel hierarchy
follow from  an infinite dimensional generalization of the open graph dichotomy.

We show that several of these applications, 
including the Hurewicz dichotomy and the Kechris-Louveau-Woodin dichotomy,
can be lifted to the generalized Baire space ${}^\kappa\kappa$,
where $\kappa$ is an uncountable cardinal with $\kappa^{<\kappa}=\kappa$.
We also obtain new applications, such as
the determinacy of V\"a\"an\"anen's perfect set game for all subsets of ${}^\kappa\kappa$ and an asymmetric version of the Baire property. 
These results extend previous work of 
L\"ucke, Motto Ros, Schlicht, V\"a\"an\"anen and the author. 
This is joint work with Philipp Schlicht.


%\begin{thebibliography}{10}

%% INSERT YOUR BIBLIOGRAPHIC ENTRIES HERE; 
%% SEE (4) BELOW FOR PROPER FORMAT.
%% EACH ENTRY MUST BEGIN WITH \bibitem{citation key}
%%
%% IF THERE ARE NO ENTRIES  
%% DELETE THE LINE ABOVE (\begin{thebibliography}{20}) 
%% AND THE LINE BELOW (\end{thebibliography})

%\end{thebibliography}


\vspace*{-0.5\baselineskip}
% this space adjustment is usually necessary after a bibliography

\end{document}


%% READ ME
%% READ ME
%% READ ME

INSTRUCTIONS FOR SUPPLYING INFORMATION IN THE CORRECT FORMAT: 

1. Author names are listed as First Last, First Last, and First Last.

\absauth{FirstName1 LastName1, FirstName2 LastName2, and FirstName3 LastName3}


2. Titles of abstracts have ONLY the first letter capitalized,
except for Proper Nouns.

\meettitle{Title of abstract with initial capital letter only, except for Proper Nouns} 


3. Affiliations and email addresses for authors of abstracts are
  listed separately.

% First author's affiliation
\affil{Department, University, Street Address, Country}
\meetemail{First author's email}
%%% NOTE: email required for at least one author
\urladdr{OPTIONAL}


% Second author's affiliation
\affil{Department, University, Street Address, Country}
\meetemail{Second author's email}
\urladdr{OPTIONAL}


% Third author's affiliation
\affil{Department, University, Street Address, Country}
% Second author's email
\meetemail{Third author's email}
\urladdr{OPTIONAL}


4. Bibliographic Entries

%%%% IF references are submitted with abstract,
%%%% please use the following formats

%%% For a Journal article
\bibitem{cite1}
{\scshape Author's Name},
{\itshape Title of article},
{\bfseries\itshape Journal name spelled out, no abbreviations},
vol.~XX (XXXX), no.~X, pp.~XXX--XXX.

%%% For a Journal article by the same authors as above,
%%% i.e., authors in cite1 are the same for cite2
\bibitem{cite2}
\bysame
{\itshape Title of article},
{\bfseries\itshape Journal},
vol.~XX (XXXX), no.~X, pp.~XX--XXX.

%%% For a book
\bibitem{cite3}
{\scshape Author's Name},
{\bfseries\itshape Title of book},
Name of series,
Publisher,
Year.

%%% For an article in proceedings
\bibitem{cite4}
{\scshape Author's Name},
{\itshape Title of article},
{\bfseries\itshape Name of proceedings}
(Address of meeting),
(First Last and First2 Last2, editors),
vol.~X,
Publisher,
Year,
pp.~X--XX.

%%% For an article in a collection
\bibitem{cite5}
{\scshape Author's Name},
{\itshape Title of article},
{\bfseries\itshape Book title}
(First Last and First2 Last2, editors),
Publisher,
Publisher's address,
Year,
pp.~X--XX.

%%% An edited book
\bibitem{cite6}
Author's name, editor. % No special font used here
{\bfseries\itshape Title of book},
Publisher,
Publisher's address,
Year.



