\documentclass[a4paper]{article} %
\usepackage{graphicx,amssymb} %

\textwidth=15cm \hoffset=-1.2cm %
\textheight=25cm \voffset=-2cm %

\pagestyle{empty} %

\date{} %

\def\keywords#1{\begin{center}{\bf Keywords}\\{#1}\end{center}} %
% Please, do not change any of the above lines
\begin{document}

% Type down your paper title
\title{Weakly Menger Ditopological Texture Spaces}

% Authors
\author{Speaker: Hafiz Ullah \\ %
\\
       Department of Computing and Technology, Abasyn University Peshawar, \\ Ring road, Patang Chowk Peshawar 25000 Pakistan\\ % Affiliation 1
      % Author 4 \\ % If any other author with different Affilation
       %University of Author 4 (Country) \\ \\ % Affiliation 2 (if needed)
       % New author \\
       % New affiliation \\
       % Add authors and affiliation as needed
       \tt{hafizwazir33@gmail.com} % Only one corresponding e-mail
       }%


\maketitle

\thispagestyle{empty}

%\begin{center}
%\emph{2000 Mathematics Subject Classification.} Primary 54A05, 54A10; Secondary 54C05, 54C08 \\
%\end{center}
\\
% The abstract
\begin{abstract}
Weakly Menger spaces were introduced by B. A. Pansera in topological spaces. We extend this idea to define weakly-s-Menger ditopological texture spaces. Also we study the interrelation between s-Menger, Weakly-s-Menger and almost-s-Menger ditopological texture spaces. We have characterized some preservations of these notion under direlation, difunction and various type of mappings

\end{abstract}

\keywords{Weakly-s-Menger spaces, almost-s-Menger spaces, ditopological texture spaces} % Write down at least 3 Keywords


{\begin{small}
\noindent{\textbf{References}}\\
$[1]$ P. Staynova, \emph{Weaker forms of the Menger property}, Quaest. Math. 35 (2012), 161–169.\\ % Format for Journal Reference
$[2]$ Lj. D. R. Ko\v{c}inac, \emph{Star-Menger and related spaces II}, Filomat 13 (1999), 129–140.\\ % Format for books
$[3]$ L. M. Brown and M. Diker, \emph{Ditopological texture spaces and intuitionistic sets}, Fuzzy Sets and Systems 98 (1998), 217-224.\\
$[4]$ L. M. Brown, R. Ertürk and ¸S. Dost, \emph{Ditopological texture spaces and fuzzy topology, II. Topological Considerations}, Fuzzy Sets and Systems 147 (2) (2004), 201-231. % Format for internet references
% etc}
\end{small}}



% \section{Introduction}
\end{document}