%% FIRST RENAME THIS FILE <yoursurname>.tex. 
%% BEFORE COMPLETING THIS TEMPLATE, SEE THE "READ ME" SECTION 
%% BELOW FOR INSTRUCTIONS. 
%% TO PROCESS THIS FILE YOU WILL NEED TO DOWNLOAD asl.cls from 
%% http://aslonline.org/abstractresources.html. 

\documentclass[bsl,meeting]{asl}

\AbstractsOn

\pagestyle{plain}

\def\urladdr#1{\endgraf\noindent{\it URL Address}: {\tt #1}.}


\newcommand{\NP}{}
%\usepackage{verbatim}

\begin{document}
\thispagestyle{empty}

%% BEGIN INSERTING YOUR ABSTRACT DIRECTLY BELOW; 
%% SEE INSTRUCTIONS (1), (2), (3), and (4) FOR PROPER FORMATS

\NP  
\absauth{Kentaro Yamamoto}
\meettitle{The strong small index property for the Fra\"iss\'e limit of
  finite Heyting algebras}
\affil{The Czech Academy of Sciences, Pod Vod\'arenskou v\v{e}\v{z}\'i 271/2, 182 07 Praha 8--Libe\v{n}, the Czech Republic.}
\meetemail{yamamoto@cs.cas.cz}
\urladdr{https://ocf.io/ykentaro/}

%% INSERT TEXT OF ABSTRACT DIRECTLY BELOW
The small index property of countable ultrahomogeneous lattice-based
structures has been established in several cases such
as the countable Boolean algebras (Truss)
and the universal homogeneous distributive lattice (Droste and
Macpherson).
In this work, the strong small index property of
the Fra\"iss\'e limit $L$ of finite Heyting algebras is proved.
This is the prime model of the model-completion of the theory of
Heyting algebras,
which is not $\omega$-categorical unlike
in the aforementioned existing literature.
The method used is an adaptation of the ad-hoc argument used by Truss
for the countable atomless Boolean algebra
and is based on the author's previous result (under review) showing
the simplicity of the automorphism group of $L$.
% (Should I say this? Should I say why not via ample generics?)


% \begin{thebibliography}{20}

% \bibitem{droste}
% {\scshape Droste},
% {\itshape Title of article},
% {\bfseries\itshape Journal name spelled out, no abbreviations},
% vol.~XX (XXXX), no.~X, pp.~XXX--XXX.


% % %% INSERT YOUR BIBLIOGRAPHIC ENTRIES HERE; 
% % %% SEE (4) BELOW FOR PROPER FORMAT.
% % %% EACH ENTRY MUST BEGIN WITH \bibitem{citation key}
% % %%
% % %% IF THERE ARE NO ENTRIES  
% % %% DELETE THE LINE ABOVE (\begin{thebibliography}{20}) 
% % %% AND THE LINE BELOW (\end{thebibliography})


% \end{thebibliography}


\vspace*{-0.5\baselineskip}
% this space adjustment is usually necessary after a bibliography

\end{document}


%% READ ME
%% READ ME
%% READ ME

INSTRUCTIONS FOR SUPPLYING INFORMATION IN THE CORRECT FORMAT: 

1. Author names are listed as First Last, First Last, and First Last.

\absauth{FirstName1 LastName1, FirstName2 LastName2, and FirstName3 LastName3}


2. Titles of abstracts have ONLY the first letter capitalized,
except for Proper Nouns.

\meettitle{Title of abstract with initial capital letter only, except for
Proper Nouns} 


3. Affiliations and email addresses for authors of abstracts are
  listed separately.

% First author's affiliation
\affil{Department, University, Street Address, Country}
\meetemail{First author's email}
%%% NOTE: email required for at least one author
\urladdr{OPTIONAL}
%
% Second author's affiliation
\affil{Department, University, Street Address, Country}
\meetemail{Second author's email}
\urladdr{OPTIONAL}
%
% Third author's affiliation
\affil{Department, University, Street Address, Country}
% Second author's email
\meetemail{Third author's email}
\urladdr{OPTIONAL}


4. Bibliographic Entries

%%%% IF references are submitted with abstract,
%%%% please use the following formats

%%% For a Journal article
\bibitem{cite1}
{\scshape Author's Name},
{\itshape Title of article},
{\bfseries\itshape Journal name spelled out, no abbreviations},
vol.~XX (XXXX), no.~X, pp.~XXX--XXX.

%%% For a Journal article by the same authors as above,
%%% i.e., authors in cite1 are the same for cite2
\bibitem{cite2}
\bysame
{\itshape Title of article},
{\bfseries\itshape Journal},
vol.~XX (XXXX), no.~X, pp.~XX--XXX.

%%% For a book
\bibitem{cite3}
{\scshape Author's Name},
{\bfseries\itshape Title of book},
Name of series,
Publisher,
Year.

%%% For an article in proceedings
\bibitem{cite4}
{\scshape Author's Name},
{\itshape Title of article},
{\bfseries\itshape Name of proceedings}
(Address of meeting),
(First Last and First2 Last2, editors),
vol.~X,
Publisher,
Year,
pp.~X--XX.

%%% For an article in a collection
\bibitem{cite5}
{\scshape Author's Name},
{\itshape Title of article},
{\bfseries\itshape Book title}
(First Last and First2 Last2, editors),
Publisher,
Publisher's address,
Year,
pp.~X--XX.

%%% An edited book
\bibitem{cite6}
Author's name, editor. % No special font used here
{\bfseries\itshape Title of book},
Publisher,
Publisher's address,
Year.

