%% FIRST RENAME THIS FILE <yoursurname>.tex. 
%% BEFORE COMPLETING THIS TEMPLATE, SEE THE "READ ME" SECTION 
%% BELOW FOR INSTRUCTIONS. 
%% TO PROCESS THIS FILE YOU WILL NEED TO DOWNLOAD asl.cls from 
%% http://aslonline.org/abstractresources.html. 


\documentclass[bsl,meeting]{asl}

\AbstractsOn

\pagestyle{plain}

\def\urladdr#1{\endgraf\noindent{\it URL Address}: {\tt #1}.}


\newcommand{\NP}{}
%\usepackage{verbatim}

\begin{document}
\thispagestyle{empty}

%% BEGIN INSERTING YOUR ABSTRACT DIRECTLY BELOW; 
%% SEE INSTRUCTIONS (1), (2), (3), and (4) FOR PROPER FORMATS

\NP  
\absauth{Tuna Altinel}
\meettitle{On the actions of finite permutation groups on groups of finite Morley rank}
\affil{Institut Camille Jordan, Université Claude Bernard Lyon 1, 43 blvd. du 11 novembre 1918, 69622, Villeurbanne cedex}
\meetemail{altinel@math.univ-lyon1.fr}

%% INSERT TEXT OF ABSTRACT DIRECTLY BELOW
Ever since the work of Borovik and Cherlin on permutation groups of finite Morley rank (\cite{BoCh08}), there has been growing
interest in faithful actions finite groups on various types of groups of finite Morley rank. This interest is due to various
motivations: classifying highly generically transitive actions on sets (\cite{AW}), highly generically transitive representations (\cite{}), 
definable actions of finite groups on groups of finite Morley rank, automorphisms of groups of finite Morley rank. In my talk,
I will give an overview of these lines of research and detail a recent result joint with Joshua Wiscons on lower bounds in the
case of faithful actions of the alternating group on a nonsolvable group of finite Morley rank that does not contain involutions.

\begin{thebibliography}{10}

%% INSERT YOUR BIBLIOGRAPHIC ENTRIES HERE; 
%% SEE (4) BELOW FOR PROPER FORMAT.
%% EACH ENTRY MUST BEGIN WITH \bibitem{citation key}
%%
%% IF THERE ARE NO ENTRIES  
%% DELETE THE LINE ABOVE (\begin{thebibliography}{20}) 
%% AND THE LINE BELOW (\end{thebibliography})
\bibitem{AW}
{\scshape Tuna Alt{\i}nel and Joshua Wiscons},
{\itshape Recognizing {$\operatorname{PGL}_3$} via generic {$4$}-transitivity},
{\bfseries\itshape Journal of the European Mathematical Society},
vol.~20 (2018), no.~6, pp.~1525--1559.

\bibitem{BerkBor18}
{\scshape Ay\c{s}e } Berkman and  Alexandre Borovik 
{\itshape Groups of finite {M}orley rank with a generically sharply multiply transitive action},
{\bfseries\itshape Journal of Algebra},
vol.~368 (2012), no.~X, pp.~237--250.

\bibitem{BerkBor21}
{\scshape Ay\c{s}e } Berkman and  Alexandre Borovik 
{\itshape Groups of finite {M}orley rank with a generically multiply transitive action on an abelian group},
{\bfseries\itshape Arxiv},
(2021), eprint 2107.09997.

\bibitem{BoCh08}
{\scshape Alexandre Borovik and Gregory Cherlin},
{\itshape Model theory with applications to algebra and analysis. {V}ol. 2},
{\bfseries\itshape Model theory with applications to algebra and analysis. {V}ol. 2}
(H. Dugald Macpherson, editors),
Cambridge Univ. Press,
Cambridge,
2008,
pp.~30--50.

\bibitem{CDW21}
{\scshape Luis Jaime Corredor and Adrien Deloro and Joshua Wiscons},
{\itshape {$\operatorname{Sym}(n)$}- and {$\operatorname{Alt}(n)$}-modules with an additive dimension},
{\bfseries\itshape Arxiv},
 (2022), eprint 2111.11498.


\end{thebibliography}


\vspace*{-0.5\baselineskip}
% this space adjustment is usually necessary after a bibliography

\end{document}


%% READ ME
%% READ ME
%% READ ME

INSTRUCTIONS FOR SUPPLYING INFORMATION IN THE CORRECT FORMAT: 

1. Author names are listed as First Last, First Last, and First Last.

\absauth{FirstName1 LastName1, FirstName2 LastName2, and FirstName3 LastName3}


2. Titles of abstracts have ONLY the first letter capitalized,
except for Proper Nouns.

\meettitle{Title of abstract with initial capital letter only, except for
Proper Nouns} 


3. Affiliations and email addresses for authors of abstracts are
  listed separately.

% First author's affiliation
\affil{Department, University, Street Address, Country}
\meetemail{First author's email}
%%% NOTE: email required for at least one author
\urladdr{OPTIONAL}
%
% Second author's affiliation
\affil{Department, University, Street Address, Country}
\meetemail{Second author's email}
\urladdr{OPTIONAL}
%
% Third author's affiliation
\affil{Department, University, Street Address, Country}
% Second author's email
\meetemail{Third author's email}
\urladdr{OPTIONAL}


4. Bibliographic Entries

%%%% IF references are submitted with abstract,
%%%% please use the following formats

%%% For a Journal article
\bibitem{cite1}
{\scshape Author's Name},
{\itshape Title of article},
{\bfseries\itshape Journal name spelled out, no abbreviations},
vol.~XX (XXXX), no.~X, pp.~XXX--XXX.

%%% For a Journal article by the same authors as above,
%%% i.e., authors in cite1 are the same for cite2
\bibitem{cite2}
\bysame
{\itshape Title of article},
{\bfseries\itshape Journal},
vol.~XX (XXXX), no.~X, pp.~XX--XXX.

%%% For a book
\bibitem{cite3}
{\scshape Borovik, Alexandre and Cherlin, Gregory},
{\bfseries\itshape Model theory with applications to algebra and analysis. {V}ol. 2},
Name of series,
Publisher,
Year.

%%% For an article in proceedings
\bibitem{cite4}
{\scshape Borovik, Alexandre and Cherlin, Gregory},
{\itshape Permutation groups of finite {M}orley rank},
{\bfseries\itshape Name of proceedings}
(Address of meeting),
(First Last and First2 Last2, editors),
vol.~X,
Publisher,
Year,
pp.~X--XX.

%%% For an article in a collection
\bibitem{BoCh08}
{\scshape Alexandre Borovik and Gregory Cherlin},
{\itshape Model theory with applications to algebra and analysis. {V}ol. 2},
{\bfseries\itshape Model theory with applications to algebra and analysis. {V}ol. 2}
(H. Dugald Macpherson, editors),
Cambridge Univ. Press,
Cambridge,
2008,
pp.~30--50.

%%% An edited book
\bibitem{cite6}
Author's name, editor. % No special font used here
{\bfseries\itshape Title of book},
Publisher,
Publisher's address,
Year.

