%% FIRST RENAME THIS FILE <yoursurname>.tex.
%% BEFORE COMPLETING THIS TEMPLATE, SEE THE "READ ME" SECTION
%% BELOW FOR INSTRUCTIONS.
%% TO PROCESS THIS FILE YOU WILL NEED TO DOWNLOAD asl.cls from
%% http://aslonline.org/abstractresources.html.


\documentclass[bsl,meeting]{asl}

\AbstractsOn

\pagestyle{plain}

\def\urladdr#1{\endgraf\noindent{\it URL Address}: {\tt #1}.}


\newcommand{\NP}{}
%\usepackage{verbatim}

\begin{document}
\thispagestyle{empty}

%% BEGIN INSERTING YOUR ABSTRACT DIRECTLY BELOW;
%% SEE INSTRUCTIONS (1), (2), (3), and (4) FOR PROPER FORMATS

\NP
\absauth{Alexander G.~Melnikov~}
\meettitle{Primitive recursive mathematics}
\affil{Victoria University of Wellington}
\meetemail{alexander.g.melnikov@gmail.com}

In my talk I will discuss the current state of the rapidly developing filed of `primitive recursive' mathematics. The subject has many different aspects. The main motivation of this framework is to understand the role of unbounded search in computable mathematics: either eliminate it when possible, or prove that without the unbounded search the result fails.
Also, primitive recursion serves as a `bridge' between the more abstract Turing computable mathematics and the perhaps more applicable polynomial-time and automatic algebra and analysis.

 Over that past several years, investigations into this direction have uncovered many deep technical issues and results that were completely `invisible' in the more general  Turing computable algebra, analysis, and infinite combinatorics. Some recent results of this sort simply have no direct analogy in computable structure theory.
In my talk I will emphasise those results and research directions in primitive recursive mathematics that either lead to counter-intuitive results or give new insights into other branches of effective mathematics. In particular, connections  with automatic structure theory  and reverse mathematics will be mentioned.



\end{document}
